
% https://www.overleaf.com/learn/latex/Sections_and_chapters
\addcontentsline{toc}{section}{참고 자료}
\section*{참고 자료}

\begin{itemize}
    \item \url{https://en.wikipedia.org/wiki/RSA_(cryptosystem)}

    \item \url{https://math.stackexchange.com/questions/1764812/carmichael-number-square-free}
    
    \item \url{https://math.stackexchange.com/questions/432162/carmichael-proof-of-at-least-3-factors}
    \item \url{https://crypto.stackexchange.com/questions/26751/rsa-with-lambdan-or-varphin}
    
    \item \url{https://en.wikipedia.org/wiki/Quicksort} \\
    \item \url{https://cs.stackexchange.com/questions/11458/ quicksort-partitioning-hoare-vs-lomuto} \\
    \item \url{https://www.acmicpc.net/blog/view/58} \\
    \item \url{https://www.youtube.com/watch?v=hq4dpyuX4Uw&list=PL52K_8WQO5oUuH06MLOrah4h05TZ4n38l&index=11} \\
    \item \url{https://en.wikipedia.org/wiki/Recursion_(computer_science)} \\
        % recursion
    \item \url{https://algs4.tistory.com/45} \\
        % h vs l testing
    \item \url{https://arxiv.org/pdf/1905.00118.pdf} \\
    \item \url{http://rohitja.in/lomuto-hoare-partitioning.html} \\


    \item \url{https://www.cs.princeton.edu/~rs/talks/QuicksortIsOptimal.pdf}
    \item \url{https://en.wikipedia.org/wiki/Dutch_national_flag_problem}\\
        % 3 way partition
    \item \url{https://en.wikipedia.org/wiki/Introsort}\\
        %introsort
    \item \url{https://www.geeksforgeeks.org/internal-details-of-stdsort-in-c/}
        %std::sort simple code
    \item \url{https://stackoverflow.com/questions/44441876/quick-sort-using-stack-in-c}
        %quicksort with stack 

    \item \url{http://fpl.cs.depaul.edu/jriely/ds1/extras/lectures/23Quicksort.pdf}
    \item \url{ https://blog.naver.com/mindo1103/221234421987}\\
    \item \url{https://blog.naver.com/mindo1103/221234421626}
\end{itemize}



\begin{thebibliography}{}
    \bibitem{reference1}
    Thomas H. Cormen, Charles E. Leiserson, Ronald L. Rivest, and Clifford Stein. Introduction to Algorithms, Second Edition. MIT Press and McGraw-Hill, 2001. ISBN 0-262-03293-7.
    
    \bibitem{reference2}
    Patterson, David A./ Hennessy, John L. Computer Organization and Design, Fourth Edition: The Hardware/Software Interface (The Morgan Kaufmann Series in Computer Architecture and Design). 2014. ISBN-13 9788994961897, ISBN-10 8994961895

    \bibitem{reference3}
    Sedgewick, R. (1978). "Implementing Quicksort programs". Comm. ACM. 21 (10): 847–857. doi:10.1145/359619.359631.

    \bibitem{reference4}
    Robert Sedgewick, Kevin Wayne Algorithms, 4th Edition, 2001 ISBN-13: 978-0321573513

    \bibitem{reference5} 이산 수학(Discrete Mathematics) (저자:Richard Johnsonbaugh)

    \bibitem{reference6} 암호학과 네트워크 보안(cryptography and network security) (저자: Behrouz A. Forouzan)

    
    \bibitem{reference7}
    Robert D. Carmichael The Theory of Numbers (1914) 

\end{thebibliography}

% testing
% std::sort